Carbonate chemistry at Ny-Ålesund

### 2021-03-22 awipev-CO2.Rmd
refined k1k2 issue; new figure added

---
title: "Carbonate chemistry at Ny-Ålesund" 
author: "Jean-Pierre Gattuso and Samir Alliouane"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  rmarkdown::html_document:
    theme: paper
    number_sections: false
---
![ ](Images/AWIPEV-Logo.jpg){width=250px}

@@

### Lueker vs Sulpis using FerryBox pCO2 and at_calc

@@

  dplyr::select(ph_s_dur_temp_4, pco2_fb, at_calc, sal_fb, temp_fb)

@@

tmp2 <- tibble(ph_s_dur_temp_4 = tmp$ph_s_dur_temp_4, pH_l = carb_l$pH, pH_s = carb_s$pH, pH_p = carb_p$pH, pH_m = carb_m$pH) %>% 

@@

            ylab = "pH @ 4°C calculated (pCO2+AT) with Lueker")

@@

            ylab = "pH @ 4°C calculated (pCO2+AT) with Sulpis") 
p <- p1 + p2
ggsave(filename = "figures/lueker-sulpis.png", plot = p, width = 20, height = 15, units = "cm")

>>>>

---
title: "Carbonate chemistry at Ny-Ålesund" 
author: "Jean-Pierre Gattuso and Samir Alliouane"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  html_document: default
  word_document: default
  pdf_document: default
  odt_document: default
---
![ ](Images/AWIPEV-Logo.jpg){width=250px}

@@

### Lueker vs Sulpis using FerryBox pCO2 and at in situ

@@

  dplyr::select(datetime, ph_s_dur_temp_4, pco2_fb, at_calc, sal_fb, temp_fb)

@@

tmp2 <- tibble(datetime = tmp$datetime, ph_s_dur_temp_4 = tmp$ph_s_dur_temp_4, 
               pH_l = carb_l$pH, pH_s = carb_s$pH, 
               pH_p = carb_p$pH, pH_m = carb_m$pH, temp_fb = tmp$temp_fb) %>% 

@@

            ylab = "pH @ 4°C calculated (pCO2+AT) with Lueker") +
  lims(x = c(8, 8.4), y = c(8, 8.4)) +
  theme(plot.title = element_text(size = 10),
        axis.text = element_text(size = 10)) +
  coord_fixed(ratio = 1)

@@

            ylab = "pH @ 4°C calculated (pCO2+AT) with Sulpis")  +
  lims(x = c(8, 8.4), y = c(8, 8.4)) +
  theme(plot.title = element_text(size = 10),
        axis.text = element_text(size = 10)) +
  coord_fixed(ratio = 1)
p3 <- tmp2 %>% 
  dplyr::mutate(delta_lueker = tmp2$ph_s_dur_temp_4 - tmp2$pH_l, 
                delta_sulpis = tmp2$ph_s_dur_temp_4 - tmp2$pH_s, 
                delta_papadimitriou = tmp2$ph_s_dur_temp_4 - tmp2$pH_p, 
                delta_millero2002 = tmp2$ph_s_dur_temp_4 - tmp2$pH_m) %>% 
  dplyr::select(-starts_with("ph_"), -datetime) %>% 
  tidyr::pivot_longer(!temp_fb, names_to = "delta", values_to = "diff") %>% 
  ggplot(aes(x = temp_fb, y = diff, col = delta)) +
  geom_point() + geom_line() +
  labs(x = "Ferrybox temperature (°C)", y = "Spec pH - calculated pH (units)") +
  theme(legend.title = element_blank())
p <- (p1 + p2) / p3
ggsave(filename = "figures/lueker-sulpis.png", plot = p, width = 25, height = 20, units = "cm")
```{r save for k1k2 report, echo=FALSE, message= FALSE, warning=FALSE}
k1k2 <- list(mean_discrete = mean_discrete, const_choice = const_choice, tmp2 = tmp2,
             errors_pco2_at = errors_pco2_at, diff_table = diff_table, 
             diff_ls_quant = diff_ls_quant)
save(k1k2, file="reports/k1k2_data.RData")
